\documentclass[twoside]{article}

\usepackage[paperwidth=140mm, paperheight=216mm]{geometry}
\usepackage{fontspec}
%\usepackage[latin1]{inputenc}
\usepackage[latin.medieval, english]{babel}
\usepackage[strict]{changepage}
\usepackage{fancyhdr}
\usepackage{paracol}
\usepackage{tableof}
\usepackage{setspace}
\usepackage{alltt}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{xstring}
\usepackage{parskip}
\usepackage{enumitem}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Mise en page %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% on numérote les nbp par page et non globalement
\usepackage[perpage]{footmisc}

% définition des en-têtes et pieds de page
\pagestyle{empty}
\fancyhead{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\setlength{\headheight}{0pt}

% la commande titres permet de changer les titres de gauche et de droite.
\newcommand{\titres}[2]{
	\renewcommand{\rightmark}{\textcolor{red}{\sc #2}}
	\renewcommand{\leftmark}{\textcolor{red}{\sc #1}}
}
\titres{}{}

% pas d'indentation
\setlength{\parindent}{0mm}

\geometry{
inner=16mm,
outer=16mm,
top=12mm,
bottom=12mm,
headsep=0mm,
}

\twosided[p]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Options gregorio %%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage[autocompile]{gregoriotex}
%\usepackage{gregoriotex}

\definecolor{gregoriocolor}{RGB}{215,65,29}

%% style général de gregorio :
% lignes rouges, commenter pour du noir
%\gresetlinecolor{gregoriocolor}

% texte <alt> (au-dessus de la portée) en rouge et en petit, avec réglage de sa position verticale
\grechangestyle{abovelinestext}{\color{gregoriocolor}\footnotesize}
\newcommand{\altraise}{-2.4mm}
\grechangedim{abovelinestextraise}{\altraise}{scalable}

% taille des initiales
\newcommand{\initialsize}[1]{
    \grechangestyle{initial}{\fontspec{ZallmanCaps}\fontsize{#1}{#1}\selectfont}
}
\newcommand{\defaultinitialsize}{32}
\initialsize{\defaultinitialsize}
% espace avant et après les initiales
\newcommand{\initialspace}[1]{
  \grechangedim{afterinitialshift}{#1}{scalable}
  \grechangedim{beforeinitialshift}{#1}{scalable}
}
\newcommand{\defaultinitialspace}{0cm}
\initialspace{\defaultinitialspace}


% on définit le système qui capture des headers pour générer des annotations
% cette commande sera appelée pour définir des abréviations ou autres substitutions
\newcommand{\resultat}{}
\newcommand{\abbrev}[3]{
  \IfSubStr{#1}{#2}{ \renewcommand{\resultat}{#3} }{}
}
\newcommand{\officepartannotation}[1]{
  \renewcommand{\resultat}{#1}
  \abbrev{#1}{ntro}{ {Intr.} }
  \abbrev{#1}{espo}{Resp.}
  \abbrev{#1}{ll}{All.}
  \abbrev{#1}{act}{Tract.}
  \abbrev{#1}{equen}{Seq.}
  \abbrev{#1}{ffert}{Off.}
  \abbrev{#1}{ommun}{Co.}
  \abbrev{#1}{ntip}{Ant.}
  \abbrev{#1}{ntic}{Cant.}
  \abbrev{#1}{ymn}{Hy.}
  \abbrev{#1}{salm}{}
  \abbrev{#1}{Toni Communes}{}
  \abbrev{#1}{yrial}{}
  \greannotation{\resultat}
}
\newcommand{\modeannotation}[1]{
  \renewcommand{\resultat}{#1}
  \abbrev{#1}{1}{ {\sc i} }
  \abbrev{#1}{2}{ {\sc ii} }
  \abbrev{#1}{3}{ {\sc iii} }
  \abbrev{#1}{4}{ {\sc iv} }
  \abbrev{#1}{5}{ {\sc v} }
  \abbrev{#1}{6}{ {\sc vi} }
  \abbrev{#1}{7}{ {\sc vii} }
  \abbrev{#1}{8}{ {\sc viii} }
  \greannotation{\resultat}
}
\gresetheadercapture{office-part}{officepartannotation}{}
\gresetheadercapture{mode}{modeannotation}{string}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Graphisme %%%%%%%%%%%%%%%%%%%%%%%%%%%
% on définit l'échelle générale

\newcommand{\echelle}{1}

% on centre les titres et on ne les numérote pas
\titleformat{\section}[block]{\Large\filcenter\sc}{}{}{}
\titleformat{\subsection}[block]{\large\filcenter\sc}{}{}{}
\titleformat{\paragraph}[block]{\filcenter\sc}{}{}{}
\setcounter{secnumdepth}{0}
% on diminue l'espace avant les titres
\titlespacing*{\paragraph}{0pt}{1.8ex plus .4ex minus .4ex}{1.2ex plus .2ex minus .2ex}

% commandes versets, repons et croix
\newcommand{\vv}{\textcolor{gregoriocolor}{\fontspec[Scale=\echelle]{Charis SIL}℣.\hspace{3mm}}}
\newcommand{\rr}{\textcolor{gregoriocolor}{\fontspec[Scale=\echelle]{Charis SIL}℟.\hspace{3mm}}}
\newcommand{\cc}{\textcolor{gregoriocolor}{\fontspec[Scale=\echelle]{FreeSerif}\symbol{"2720}~}}
\renewcommand{\aa}{\textcolor{gregoriocolor}{\fontspec[Scale=\echelle]{Charis SIL}\Abar.\hspace{3mm}}}

% commandes diverses
\newcommand{\antiphona}{\textcolor{gregoriocolor}{\noindent Antiphona.\hspace{4mm}}}
\newcommand{\antienne}{\textcolor{gregoriocolor}{\noindent Antienne.\hspace{4mm}}}
\newcommand{\rubrique}[1]{\textcolor{gregoriocolor}{\emph{#1}}}
\newcommand{\saut}{\hspace{1cm}}
\newcommand{\capsaut}{\hspace{3mm}}
% pour affichier 1 en rouge et un peu d'espace
\newcommand{\un}{{\color{gregoriocolor} 1~~~}}

% abréviations
\newcommand{\tpalleluia}{\rubrique{(T.P.} \mbox{Allelúia.\rubrique{)}}}
\newcommand{\tpalleluiafr}{\rubrique{(T.P.} \mbox{Alléluia.\rubrique{)}}}

\newcommand{\tqomittitur}{{\small \rubrique{(In Tempore Quadragesimæ ommittitur} Allelúia.\rubrique{)}}}
\newcommand{\careme}{{\small \rubrique{(Pendant le Carême on omet l'}Alléluia.\rubrique{)}}}

% environnement hymne : alltt + normalfont + marges custom
\newenvironment{hymne}
  {
  \begin{adjustwidth}{1.6cm}{1mm}
  \begin{alltt}\normalfont
  }
  {
  \end{alltt}
  \end{adjustwidth}
  }
  
% la commande \u permet de souligner les inflexions
\let\u\textbf

% on définit la police par défaut
\setmainfont[Ligatures=TeX, Scale=\echelle]{Charis SIL}
%renderer=ICU a l'air de ne plus marcher...
%\setmainfont[Renderer=ICU, Ligatures=TeX, Scale=\echelle]{Charis SIL}
\setstretch{0.9}

\begin{document}

\begin{center}\begin{doublespace}

\vspace*{3cm}

{\fontspec[Scale=\echelle]{Futura Book}
\MakeUppercase{\Large Dominica VII post Pentecosten \\ ad I. Vesperas}\\
juxta usum antiquiorem ritus romani}

\vspace{5cm}

{\fontspec[Scale=\echelle]{Futura Book}
\MakeUppercase{\Large First Vespers of the 7\textsuperscript{th}~Sunday \\ after Pentecost}\\
according to the more ancient use of the Roman Rite
}


\end{doublespace}\end{center}

\newpage

\sloppy

\begin{paracol}[1]{2}

\begin{center}\begin{doublespace}

{\fontspec[Scale=\echelle]{Futura Book}
\MakeUppercase{\Large Dominica VII post Pentecosten \\ ad I. Vesperas}\\
juxta usum antiquiorem ritus romani}
\end{doublespace}\end{center}

\gresetinitiallines{0}
\gregorioscore{gabc/or--deus_in_adjutorium}
\gresetinitiallines{1}

~~

\switchcolumn

\selectlanguage{english}
\begin{center}\begin{doublespace}
{\fontspec[Scale=\echelle]{Futura Book}
\MakeUppercase{\Large First Vespers of the 7\textsuperscript{th}~Sunday \\ after Pentecost}\\
according to the more ancient use of the Roman Rite
}
\end{doublespace}\end{center}

~~

~~

\vv O God, \cc come to my assistance;

\rr O Lord, make haste to help me.

\vv Glory be to the Father, and to the Son, * and to the Holy Ghost.

\rr As it was in the beginning, is now, * and ever shall be, world without end. Amen. Alleluia.

\switchcolumn*

\paragraph{Psalmus 143 - I}

\gregorioscore{gabc/1an}

\begin{enumerate}[wide, itemsep=0mm, labelwidth=!, labelindent=0pt, label=\color{gregoriocolor}\theenumi]
\selectlanguage{latin}
\item Benedíctus Dóminus, Deus meus, qui docet manus meas \textit{ad} \textbf{prǽ}lium,~* et dígitos me\textit{os} \textit{ad} \textbf{bel}lum.
\item Misericórdia mea, et refúgi\textit{um} \textbf{me}um :~* suscéptor meus, et libe\textit{rá}\textit{tor} \textbf{me}us :
\item Protéctor meus, et in ipso \textit{spe}\textbf{rá}vi :~* qui subdit pópulum \textit{me}\textit{um} \textbf{sub} me.
\item Dómine, quid est homo quia innotuís\textit{ti} \textbf{e}i ?~* aut fílius hóminis, quia ré\textit{pu}\textit{tas} \textbf{e}um ?
\item Homo vanitáti sími\textit{lis} \textbf{fac}tus est :~* dies ejus sicut um\textit{bra} \textit{præ}\textbf{tér}eunt.
\item Dómine, inclína cælos tuos, et \textit{de}\textbf{scén}de :~* tange montes, et \textit{fu}\textit{mi}\textbf{gá}bunt.
\item Fúlgura coruscatiónem, et dissipá\textit{bis} \textbf{e}os :~* emítte sagíttas tuas, et contur\textit{bá}\textit{bis} \textbf{e}os.
\item Emítte manum tuam de alto,~† éripe me, et líbera me de a\textit{quis} \textbf{mul}tis~:~* de manu filiórum a\textit{li}\textit{e}\textbf{nó}rum.
\item Quorum os locútum est va\textit{ni}\textbf{tá}tem~:~* et déxtera eórum, déxtera in\textit{i}\textit{qui}\textbf{tá}tis.
\item Glória Patri, \textit{et} \textbf{Fí}lio ,~* et Spirí\textit{tu}\textit{i} \textbf{Sanc}to.
\item Sicut erat in princípio, et nunc, \textit{et} \textbf{sem}per,~* et in sǽcula sæcu\textit{ló}\textit{rum}. \textbf{A}men.
\end{enumerate}

\switchcolumn


\paragraph{Psalm 143 - I}
\aa Blessed be the Lord * my support, and my deliverer.

\gregorioscore{gabc/6_lib}

\begin{enumerate}[wide, itemsep=0mm, labelwidth=!, labelindent=0pt, label=\color{gregoriocolor}\theenumi]
\item Blessed be the Lord my God, who teacheth my hands to fight, * and my fingers to war.
\item My mercy, and my refuge: * my support, and my deliverer:
\item My protector, and I have hoped in him: * who subdueth my people under me.
\item Lord, what is man, that thou art made known to him? * or the son of man, that thou makest account of him?
\item Man is like to vanity: * his days pass away like a shadow.
\item Lord, bow down thy heavens and descend: * touch the mountains, and they shall smoke.
\item Send forth lightning, and thou shalt scatter them: * shoot out thy arrows, and thou shalt trouble them.
\item Put forth thy hand from on high, take me out, and deliver me from many waters: * from the hand of strange children:
\item Whose mouth hath spoken vanity: * and their right hand is the right hand of iniquity.
\end{enumerate}

\switchcolumn*
\paragraph{Psalmus 143 - II}

\gregorioscore{gabc/2an}


\begin{enumerate}[wide, itemsep=0mm, labelwidth=!, labelindent=0pt, label=\color{gregoriocolor}\theenumi]
\item Deus, cánticum novum cantábo \textbf{ti}bi:~* in psaltério, decachórdo \textit{psal}\textit{lam} \textbf{ti}bi.
\item Qui das salútem \textbf{ré}gibus :~* qui redemísti David, servum tuum, de gládio malígno : \textit{é}\textit{ri}\textbf{pe} me.
\item Et érue me de manu filiórum alienórum,~† quorum os locútum est vani\textbf{tá}tem :~* et déxtera eórum, déxtera in\textit{i}\textit{qui}\textbf{tá}tis.
\item Quorum fílii, sicut novéllæ plantati\textbf{ó}nes~* in juven\textit{tú}\textit{te} \textbf{su}a.
\item Fíliæ eórum com\textbf{pó}sitæ :~* circumornátæ ut simili\textit{tú}\textit{do} \textbf{tem}pli.
\item Promptuária eórum \textbf{ple}na :~* eructántia ex \textit{hoc} \textit{in} \textbf{il}lud.
\item Oves eórum fœtósæ, abundántes in egréssibus \textbf{su}is :~* boves e\textit{ó}\textit{rum} \textbf{cras}sæ.
\item Non est ruína macériæ, neque \textbf{tráns}itus :~* neque clamor in platé\textit{is} \textit{e}\textbf{ó}rum.
\item Beátum dixérunt pópulum, cui \textbf{hæc} sunt :~* beátus pópulus, cujus Dóminus \textit{De}\textit{us} \textbf{e}jus.
\item Glória Patri, et \textbf{Fí}lio,~* et Spirí\textit{tu}\textit{i} \textbf{Sanc}to.
\item Sicut erat in princípio, et nunc, et \textbf{sem}per,~* et in sǽcula sæcu\textit{ló}\textit{rum}. \textbf{A}men.
\end{enumerate}

\switchcolumn

\paragraph{Psalm 143 - II}
\aa Happy is that people * whose God is the Lord.

\gregorioscore{gabc/8_c}


\begin{enumerate}[wide, itemsep=0mm, labelwidth=!, labelindent=0pt, label=\color{gregoriocolor}\theenumi]
\item To thee, O God, I will sing a new canticle: * on the psaltery and an instrument of ten strings I will sing praises to thee.
\item Who givest salvation to kings: * who hast redeemed thy servant David from the malicious sword: Deliver me,
\item And rescue me out of the hand of strange children; whose mouth hath spoken vanity: * and their right hand is the right hand of iniquity:
\item Whose sons are as new plants * in their youth:
\item Their daughters decked out, * adorned round about after the similitude of a temple:
\item Their storehouses full, * flowing out of this into that.
\item Their sheep fruitful in young, abounding in their goings forth: * their oxen fat.
\item There is no breach of wall, nor passage, * nor crying out in their streets.
\item They have called the people happy, that hath these things: * but happy is that people whose God is the Lord.
\end{enumerate}
\newpage
\switchcolumn*

\paragraph{Psalmus 144 - I}

\gregorioscore{gabc/3an}


\begin{enumerate}[wide, itemsep=0mm, labelwidth=!, labelindent=0pt, label=\color{gregoriocolor}\theenumi]
\item Exaltábo te, \textbf{De}us \textbf{me}us, rex:~* et benedícam nómini tuo in sǽculum, et in sǽ\textit{cu}\textit{lum} \textbf{sǽ}culi.
\item Per síngulos dies bene\textbf{dí}cam \textbf{ti}bi :~* et laudábo nomen tuum in sǽculum, et in sǽ\textit{cu}\textit{lum} \textbf{sǽ}culi.
\item Magnus Dóminus, et lau\textbf{dá}bilis \textbf{ni}mis :~* et magnitúdinis ejus \textit{non} \textit{est} \textbf{fi}nis.
\item Generátio et generátio laudábit \textbf{ó}pera \textbf{tu}a :~* et poténtiam tuam pro\textit{nun}\textit{ti}\textbf{á}bunt.
\item Magnificéntiam glóriæ sanctitátis \textbf{tu}æ lo\textbf{quén}tur :~* et mirabília tu\textit{a} \textit{nar}\textbf{rá}bunt.
\item Et virtútem terribílium tu\textbf{ó}rum \textbf{di}cent :~* et magnitúdinem tu\textit{am} \textit{nar}\textbf{rá}bunt.
\item Memóriam abundántiæ suavitátis tuæ \textbf{e}ruc\textbf{tá}bunt :~* et justítia tua \textit{ex}\textit{sul}\textbf{tá}bunt.
\item Glória \textbf{Pa}tri, et \textbf{Fí}lio,~* et Spirí\textit{tu}\textit{i} \textbf{Sanc}to.
\item Sicut erat in princípio, et \textbf{nunc}, et \textbf{sem}per,~* et in sǽcula sæcu\textit{ló}\textit{rum}. \textbf{A}men.
\end{enumerate}

\switchcolumn

\paragraph{Psalm 144 - I}

\aa For the Lord is great * and exceedingly to be praised: His greatness has no end.

\gregorioscore{gabc/1_a3}

\begin{enumerate}[wide, itemsep=0mm, labelwidth=!, labelindent=0pt, label=\color{gregoriocolor}\theenumi]

\item I will extol thee, O God my king: * and I will bless thy name for ever; yea, for ever and ever.
\item Every day will I bless thee: * and I will praise thy name for ever; yea, for ever and ever.
\item Great is the Lord, and greatly to be praised: * and of his greatness there is no end.
\item Generation and generation shall praise thy works: * and they shall declare thy power.
\item They shall speak of the magnificence of the glory of thy holiness: * and shall tell thy wondrous works.
\item And they shall speak of the might of thy terrible acts: * and shall declare thy greatness.
\item They shall publish the memory of the abundance of thy sweetness: * and shall rejoice in thy justice.
\end{enumerate}

\switchcolumn*
\paragraph{Psalmus 144 - II}

\gregorioscore{gabc/4an}


\begin{enumerate}[wide, itemsep=0mm, labelwidth=!, labelindent=0pt, label=\color{gregoriocolor}\theenumi]

\item Miserátor, et miséricors \textbf{Dó}minus:~* pátiens, et mul\textit{tum} \textit{mi}\textbf{sé}ricors.
\item Suávis Dóminus uni\textbf{vér}sis :~* et miseratiónes ejus super ómnia ó\textit{pe}\textit{ra} \textbf{e}jus.
\item Confiteántur tibi, Dómine, ómnia ópera \textbf{tu}a :~* et sancti tui bene\textit{dí}\textit{cant} \textbf{ti}bi.
\item Glóriam regni tui \textbf{di}cent :~* et poténtiam tu\textit{am} \textit{lo}\textbf{quén}tur :
\item Ut notam fáciant fíliis hóminum poténtiam \textbf{tu}am :~* et glóriam magnificéntiæ \textit{re}\textit{gni} \textbf{tu}i.
\item Regnum tuum regnum ómnium sæcu\textbf{ló}rum :~* et dominátio tua in omni generatióne et gene\textit{ra}\textit{ti}\textbf{ó}nem.
\item Glória Patri, et \textbf{Fí}lio,~* et Spirí\textit{tu}\textit{i} \textbf{Sanc}to.
\item Sicut erat in princípio, et nunc, et \textbf{sem}per,~* et in sǽcula sæcu\textit{ló}\textit{rum}. \textbf{A}men.
\end{enumerate}

\switchcolumn

\paragraph{Psalm 144 - II}

\aa The Lord is sweet * to all: and his tender mercies are over all his works.

\gregorioscore{gabc/8_G}

\begin{enumerate}[wide, itemsep=0mm, labelwidth=!, labelindent=0pt, label=\color{gregoriocolor}\theenumi]
\item The Lord is gracious and merciful: * patient and plenteous in mercy.
\item The Lord is sweet to all: * and his tender mercies are over all his works.
\item Let all thy works, O Lord, praise thee: * and let thy saints bless thee.
\item They shall speak of the glory of thy kingdom: * and shall tell of thy power:
\item To make thy might known to the sons of men: * and the glory of the magnificence of thy kingdom.
\item Thy kingdom is a kingdom of all ages: * and thy dominion endureth throughout all generations.
\end{enumerate}

\switchcolumn*
\paragraph{Psalmus 144 - III}

\gregorioscore{gabc/5an}


\begin{enumerate}[wide, itemsep=0mm, labelwidth=!, labelindent=0pt, label=\color{gregoriocolor}\theenumi]
\setcounter{enumi}{1}
\item Allevat Dóminus om\textit{nes} \textit{qui} \textbf{cór}ruunt:~* et érigit omnes e\textbf{lí}sos.
\item Oculi ómnium in te \textit{spe}\textit{rant}, \textbf{Dó}mine :~* et tu das escam illórum in témpore oppor\textbf{tú}no.
\item Aperis tu \textit{ma}\textit{num} \textbf{tu}am :~* et imples omne ánimal benedicti\textbf{ó}ne.
\item Justus Dóminus in ómnibus \textit{vi}\textit{is} \textbf{su}is :~* et sanctus in ómnibus opéribus \textbf{su}is.
\item Prope est Dóminus ómnibus invocán\textit{ti}\textit{bus} \textbf{e}um :~* ómnibus invocántibus eum in veri\textbf{tá}te.
\item Voluntátem timéntium se fáciet :~† et deprecatiónem eó\textit{rum} \textit{ex}\textbf{áu}diet :~* et salvos fáciet \textbf{e}os.
\item Custódit Dóminus omnes \textit{di}\textit{li}\textbf{gén}tes se :~* et omnes peccatóres dis\textbf{pér}det.
\item Laudatiónem Dómini loqué\textit{tur} \textit{os} \textbf{me}um :~* et benedícat omnis caro nómini sancto ejus in sǽculum, et in sǽculum \textbf{sǽ}culi.
\item Glória Pa\textit{tri}, \textit{et} \textbf{Fí}lio,~* et Spirítui \textbf{Sanc}to.
\item Sicut erat in princípio, et \textit{nunc}, \textit{et} \textbf{sem}per,~* et in sǽcula sæculórum. \textbf{A}men.
\end{enumerate}

\switchcolumn

\paragraph{Psalm 144 - III}
\aa The Lord is faithful * in all his words: and holy in all his works.

\gregorioscore{gabc/4_la_g}

\begin{enumerate}[wide, itemsep=0mm, labelwidth=!, labelindent=0pt, label=\color{gregoriocolor}\theenumi]
\item The Lord is faithful in all his words: and holy in all his works.
\item The Lord lifteth up all that fall: * and setteth up all that are cast down.
\item The eyes of all hope in thee, O Lord: * and thou givest them meat in due season.
\item Thou openest thy hand, * and fillest with blessing every living creature.
\item The Lord is just in all his ways: * and holy in all his works.
\item The Lord is nigh unto all them that call upon him: * to all that call upon him in truth.
\item He will do the will of them that fear him: * and he will hear their prayer, and save them.
\item The Lord keepeth all them that love him; * but all the wicked he will destroy.
\item My mouth shall speak the praise of the Lord: * and let all flesh bless his holy name for ever; yea, for ever and ever.
\end{enumerate}
\newpage
\switchcolumn*

\paragraph{Capitulum}
O Altitúdo divitiárum sapiéntiæ, et sciéntiæ Dei : † quam incomprehensibília sunt iudícia eius, * et investigábiles viæ eius!

\gresetinitiallines{0}
\gregorioscore{gabc/or--deo_gratias_capitulum}
\gresetinitiallines{1}

\switchcolumn

\paragraph{Little Chapter}
\rubrique{Rom. 11, 33} \capsaut O the depth of the riches of the wisdom and of the knowledge of God! How incomprehensible are his judgments, and how unsearchable his ways!\\
\rr Thanks be to God.

\switchcolumn*

\paragraph{Hymnus}

\gregorioscore{gabc/hy}

\switchcolumn

\paragraph{Hymn}
\begin{alltt}\normalfont
              As fades the glowing orb of day,
              To thee, great source of light, we pray;
              Blest Three in One, to every heart
              Thy beams of life and love impart.

              At early dawn, at close of day,
              To thee our vows we humbly pay;
              May we, mid joys that never end,
              With thy bright saints in homage bend.

              To God the Father, and the Son,
              And Holy Spirit, Three in One,
              Be endless glory, as before
              The world began, so evermore.
              Amen.
\end{alltt}
\newpage
\switchcolumn*
\gresetinitiallines{0}
\gregorioscore{gabc/VespertinaOratio}
\gresetinitiallines{1}
\switchcolumn

\vv Let the evening prayer ascend unto thee, O Lord.

\rr And let there descend upon us thy mercy.

\switchcolumn*

\paragraph{Canticum Beatæ Mariæ Virginis}

\gregorioscore{gabc/mag_ant}


\switchcolumn

\paragraph{Canticle of the Blessed Virgin Mary}

\aa Nathan the Prophet * anointed Solomon King in Gihon, and they went up with joy, and cried, saying: May the King live for ever.

\gregorioscore{gabc/M}
\gresetinitiallines{0}

\switchcolumn*

\begin{enumerate}[wide, itemsep=0mm, labelwidth=!, labelindent=0pt, label=\color{gregoriocolor}\theenumi]
\item \textit{Ma}\textbf{gní}\textbf{fi}cat~* ánima \textit{me}\textit{a} \textbf{Dó}minum.
\item Et exsultávit \textit{spí}\textit{ri}\textit{tus} \textbf{me}us~* in Deo salu\textit{tá}\textit{ri} \textbf{me}o.
\item Quia respéxit humilitátem \textit{an}\textit{cíl}\textit{læ} \textbf{su}æ :~* ecce enim ex hoc beátam me dicent omnes gene\textit{ra}\textit{ti}\textbf{ó}nes.
\item Quia fecit mihi \textit{ma}\textit{gna} \textit{qui} \textbf{pot}\textbf{ens} est :~* et sanctum \textit{no}\textit{men} \textbf{e}jus.
\item Et misericórdia ejus a progéni\textit{e} \textit{in} \textit{pro}\textbf{gé}\textbf{ni}es~* timén\textit{ti}\textit{bus} \textbf{e}um.
\item Fecit poténtiam in \textit{brá}\textit{chi}\textit{o} \textbf{su}o :~* dispérsit supérbos mente \textit{cor}\textit{dis} \textbf{su}i.
\item Depósuit pot\textit{én}\textit{tes} \textit{de} \textbf{se}de,~* et exal\textit{tá}\textit{vit} \textbf{hú}miles.
\item Esuriéntes \textit{im}\textit{plé}\textit{vit} \textbf{bo}nis :~* et dívites dimí\textit{sit} \textit{in}\textbf{á}nes.
\item Suscépit Israël \textit{pú}\textit{e}\textit{rum} \textbf{su}um,~* recordátus misericór\textit{di}\textit{æ} \textbf{su}æ.
\item Sicut locútus est \textit{ad} \textit{pa}\textit{tres} \textbf{nos}tros,~* Abraham et sémini e\textit{jus} \textit{in} \textbf{sǽ}cula.
\item Glória \textit{Pa}\textit{tri}, \textit{et} \textbf{Fí}\textbf{li}o,~* et Spirí\textit{tu}\textit{i} \textbf{Sanc}to.
\item Sicut erat in princípio, \textit{et} \textit{nunc}, \textit{et} \textbf{sem}per,~* et in sǽcula sæcu\textit{ló}\textit{rum}. \textbf{A}men.
\end{enumerate}
\switchcolumn
\begin{enumerate}[wide, itemsep=0mm, labelwidth=!, labelindent=0pt, label=\color{gregoriocolor}\theenumi]
\item My soul \cc * doth magnify the Lord.
\item And my spirit hath rejoiced * in God my Saviour.
\item Because he hath regarded the humility of his handmaid; * for behold from henceforth all generations shall call me blessed.
\item Because he that is mighty, hath done great things to me; * and holy is his name.
\item And his mercy is from generation unto generations, * to them that fear him.
\item He hath shewed might in his arm: * he hath scattered the proud in the conceit of their heart.
\item He hath put down the mighty from their seat, * and hath exalted the humble.
\item He hath filled the hungry with good things; * and the rich he hath sent empty away.
\item He hath received Israel his servant, * being mindful of his mercy:
\item As he spoke to our fathers, * to Abraham and to his seed for ever.
\end{enumerate}
\newpage
\switchcolumn*

\vv Dóminus vobíscum. \\
\rr Et cum spíritu tuo.

Orémus.\\
Largíre, quǽsumus, Dómine, fidélibus tuis indulgéntiam placátus et pacem: ut páriter ab ómnibus mundéntur offénsis, et secúra tibi mente desérviant.
Per Dóminum nostrum Iesum Christum, Fílium tuum: qui tecum vivit et regnat in unitáte Spíritus Sancti, Deus, per ómnia sǽcula sæculórum. \\
\rr Amen.

\switchcolumn

\vv The Lord be with you. \\
\rr And with thy spirit.

Let us pray. \\
O God, Whose never-failing Providence ordereth all things both in heaven and earth, we humbly beseech thee to put away from us all hurtful things, and to give us those things which be profitable for us.
Through Jesus Christ, thy Son our Lord, Who liveth and reigneth with thee, in the unity of the Holy Ghost, God, world without end.
\rr Amen.

\switchcolumn*

\vv Dóminus vobíscum. \\
\rr Et cum spíritu tuo.

~~

\gregorioscore{gabc/or--benedicamus_domino}

\switchcolumn

\vv The Lord be with you.\\
\rr And with thy spirit.

~~

\vv Let us bless the Lord. \\
\rr Thanks be to God.

\switchcolumn*

~~

\vv Fidélium ánimæ per misericórdiam Dei requiéscant in pace. \\
\rr Amen.

\switchcolumn

~~

\vv May the souls of the faithful, through the mercy of God, rest in peace. \\
\rr Amen.

~~

\emph{Translation of the \emph{Salve Regina}, next page:}

\begin{alltt}\normalfont
    Hail holy Queen, Mother of Mercy, 
    Our life, our sweetness, and our hope.
    To thee do we cry, poor banished children of Eve.
    To thee do we send up our sighs, mourning and weeping 
    In this valley of tears.
    
    Turn then, most gracious Advocate, thine eyes of mercy toward us.
    And after this our exile show unto us 
    The blessed fruit of thy womb, Jesus.
    O clement, O loving, O sweet Virgin Mary.
\end{alltt}

\switchcolumn*

\begin{center}
{\small MMXXII a Matthias Bry editum}
\end{center}

\end{paracol}

\newpage

\gregorioscore{gabc/salve_solemn}


\end{document}